---
title: "EDA"
author: "m.ooki"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 4.5
    fig_caption: true
    theme: cosmo
    highlight: tango
    code_folding: hide
    code_download: true
---

# Summary 

* Task : 将来48時間の(2018/5/1-31)のair quality を予測する

* Predict : 2つの市で合計48箇所を将来48時間（1時間ごと）の3指標を予測。48 * 48 = 2304 
    - the concentration of PM2.5/PM10/O3 for 35 stations in Beijing 
    - the concentration of PM2.5/PM10 for 13 stations in London

* 訓練データ
   - 過去のair quality
   - 過去のMeorogical (weather) ?

* 2018/4/1-30のデータはAPIで取得するみたい


# Preparations {.tabset .tabset-fade .tabset-pills}

## libraries

```{r, message=F, warning=F}
options(scipen=100)
library(data.table)
library(dplyr)
library(magrittr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(corrplot, lib.loc="~/R/x86_64-pc-linux-gnu-library/3.5/")
#library(ggforce, lib.loc="~/R/x86_64-pc-linux-gnu-library/3.5/") # facet_zoom
library(scales)
library(leaflet, lib.loc = "~/R/x86_64-pc-linux-gnu-library/3.5/")
library(pheatmap, lib.loc = "~/R/x86_64-pc-linux-gnu-library/3.5/")
```

## vars

```{r}
DIR_INPUT <- "/mnt/data/kddcup2018/input"
DIR_OUTPUT_CLEAN <- "/mnt/data/kddcup2018/input_clean"
DIR_API_INPUT <- "/mnt/data/kddcup2018/input_api"
```

## Util function

```{r}
source("~/kddcup2018/utils/ggplot.R")
source("~/kddcup2018/utils/color.R")
source("~/kddcup2018/utils/time.R")
```

## Data Loading

```{r}
df.bei.aq1 <- fread(paste0(DIR_INPUT,"/beijing_17_18_aq.csv"), header = T)
df.bei.aq2 <- fread(paste0(DIR_INPUT,"/beijing_201802_201803_aq.csv"), header = T)
df.bei.aq <- bind_rows(df.bei.aq1, df.bei.aq2) %>% arrange(stationId)
rm(df.bei.aq1, df.bei.aq2)
df.bei.obs.meo <- fread(paste0(DIR_INPUT,"/beijing_17_18_meo.csv"), header = T)
df.bei.obs.meo.map <- select(df.bei.obs.meo, station_id, longitude, latitude) %>% unique()
df.bei.obs.meo.2 <- fread(paste0(DIR_INPUT,"/beijing_201802_201803_me.csv"), header = T) %>% left_join(df.bei.obs.meo.map, by = "station_id")
df.bei.obs.meo <- bind_rows(df.bei.obs.meo, df.bei.obs.meo.2) %>% arrange(station_id)
rm(df.bei.obs.meo.2, df.bei.obs.meo.map)
df.bei.grid.meo <- fread(paste0(DIR_INPUT,"/Beijing_historical_meo_grid.csv"), header = T)
df.bei.station <- fread(paste0(DIR_INPUT,"/Beijing_AirQuality_Stations_en.csv"), header = T)
```

```{r}
df.lon.station <- fread(paste0(DIR_INPUT,"/London_AirQuality_Stations.csv"), header = T)
df.lon.grid.meo <- fread(paste0(DIR_INPUT,"/London_historical_meo_grid.csv"), header = T)
df.lon.aq1 <- fread(paste0(DIR_INPUT,"/London_historical_aqi_forecast_stations_20180331.csv"), header = T)
df.lon.aq2 <- fread(paste0(DIR_INPUT,"/London_historical_aqi_other_stations_20180331.csv"), header = T)
```

```{r}
df.submit <- fread(paste0(DIR_INPUT,"/sample_submission.csv"), header = T, logical01 = F)
```

## API Data Loading

```{r}
API_ENDTIME <- format(Sys.time() - (1 * 60 * 60 + 9 * 60 * 60), "%Y-%m-%d-%H")
SPAN <- paste0("2018-03-31-00_",API_ENDTIME)
df.api.bei.aq <- fread(paste0(DIR_API_INPUT,"/",SPAN,"/bj_airquality.csv"), header = T)
df.api.ld.aq <- fread(paste0(DIR_API_INPUT,"/",SPAN,"/ld_airquality.csv"), header = T)
df.api.bei.obs.meo <- fread(paste0(DIR_API_INPUT,"/",SPAN,"/bj_meteorology.csv"), header = T)
df.api.bei.grid.meo <- fread(paste0(DIR_API_INPUT,"/",SPAN,"/bj_grid_meteorology.csv"), header = T)
df.api.ld.grid.meo <- fread(paste0(DIR_API_INPUT,"/",SPAN,"/ld_grid_meteorology.csv"), header = T)
```

# Data Cleansing {.tabset .tabset-fade .tabset-pills}

## Names

```{r}
names(df.bei.aq)[1] <- "station_id"
df.bei.aq %<>% select(utc_time, everything())
names(df.bei.station) <- c("area","station_id","long","lati") 
names(df.bei.obs.meo)[2:3] <- c("long","lati")
names(df.bei.grid.meo)[2:3] <- c("long","lati")
names(df.bei.grid.meo)[9] <- "wind_speed"
```

```{r}
names(df.lon.aq1)[2:6] <- c("utc_time", "station_id", "PM2.5","PM10", "NO2")
names(df.lon.aq2)[1:5] <- c("station_id", "utc_time", "PM2.5","PM10", "NO2") 
df.lon.aq2 %<>% select(utc_time, everything())
names(df.lon.station) <- c("station_id","api_data","need_prediction","historical_data","lati","long","area","area_name")
names(df.lon.grid.meo)[2:3] <- c("long","lati")
names(df.lon.grid.meo)[9] <- "wind_speed"
```

```{r}
names(df.api.bei.aq)[3:9] <- c("utc_time","PM2.5","PM10","NO2","CO","O3","SO2")
names(df.api.ld.aq)[3:9] <- c("utc_time","PM2.5","PM10","NO2","CO","O3","SO2")
names(df.api.bei.grid.meo)[2:3] <- c("stationName", "utc_time")
names(df.api.bei.obs.meo)[2:3] <- c("stationName", "utc_time")
names(df.api.ld.grid.meo)[2:3] <- c("stationName", "utc_time")
```

## Delete unused column

```{r}
df.lon.aq1 %<>% select(-V1)
df.lon.aq2 %<>% select(-V6, -V7)
```

```{r}
df.api.bei.aq %<>% select(-id)
df.api.ld.aq %<>% select(-id, -CO, -O3, -SO2)
df.api.bei.obs.meo %<>% select(-id)
df.api.bei.grid.meo %<>% select(-id)
df.api.ld.grid.meo %<>% select(-id)
```

## Time Convert

```{r}
df.bei.aq %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S")) 
df.bei.obs.meo %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S")) 
df.bei.grid.meo %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S")) 
df.lon.aq1 %<>% mutate(utc_time = parse_date_time(utc_time, "%Y/%m/%d %H:%M")) 
df.lon.aq2 %<>% mutate(utc_time = parse_date_time(utc_time, "%Y/%m/%d %H:%M")) 
df.lon.grid.meo %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S"))
```

```{r}
df.api.bei.aq %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S"))
df.api.bei.obs.meo %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S"))
df.api.bei.grid.meo %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S"))

df.api.ld.aq %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S"))
df.api.ld.grid.meo %<>% mutate(utc_time = parse_date_time(utc_time, "%Y-%m-%d %H:%M:%S"))
```

## Beijing the nearest Obs point

```{r}
df.bei.station %>% select(station_id, long, lati) %>% mutate(group = "target") -> tmp1
df.bei.obs.meo %>% select(station_id, long, lati) %>%  unique() %>% mutate(group = "obs") -> tmp2
df.tmp <- bind_rows(tmp1, tmp2) %>% mutate(number = row_number())
dist.matrix <- df.tmp %>% select(long, lati) %>% as.matrix() %>% dist() 
reshape::melt(as.matrix(dist.matrix), varnames = c("row", "col")) %>%
  filter(value != 0) %>%
  filter(col > 36) %>% #35までがtargetなのでそれを除く
  filter(row <= 35) %>% #35までがtargetなのでそれを除く
  group_by(row) %>%
  dplyr::summarise(col = col[which.min(value)], min_dist = min(value)) -> df.min.dist

df.tmp %>%
  select(station_id, number) %>%
  inner_join(df.min.dist, by = c("number" = "row")) %>%
  select(-number) -> tmp1
df.tmp %>%
  select(station_id, number) %>%
  setnames("station_id", "nearest") %>%
  inner_join(df.min.dist, by = c("number" = "col")) %>%
  select(nearest, number) %>%
  setnames("number", "col") -> tmp2
tmp1 %>%
  inner_join(tmp2, by = "col") %>%
  select(station_id, nearest) %>%
  unique() -> df.bei.obs.nearest
rm(tmp1, tmp2, df.tmp)
```


## Beijing the nearest Grid point

```{r}
df.bei.station %>% select(station_id, long, lati) %>% mutate(group = "target") -> tmp1
df.bei.grid.meo %>% select(stationName, long, lati) %>% unique() %>% mutate(group = "grid") %>% rename(station_id = "stationName") -> tmp2
df.tmp <- bind_rows(tmp1, tmp2) %>% mutate(number = row_number())
dist.matrix <- df.tmp %>% select(long, lati) %>% as.matrix() %>% dist() 
reshape::melt(as.matrix(dist.matrix), varnames = c("row", "col")) %>%
  filter(value != 0) %>%
  filter(col > 36) %>% #35までがtargetなのでそれを除く
  filter(row <= 35) %>% #35までがtargetなのでそれを除く
  group_by(row) %>%
  dplyr::summarise(col = col[which.min(value)], min_dist = min(value)) -> df.min.dist

df.tmp %>%
  select(station_id, number) %>%
  inner_join(df.min.dist, by = c("number" = "row")) %>%
  select(-number) -> tmp1
df.tmp %>%
  select(station_id, number) %>%
  setnames("station_id", "nearest") %>%
  inner_join(df.min.dist, by = c("number" = "col")) %>%
  select(nearest, number) %>%
  setnames("number", "col") -> tmp2
tmp1 %>%
  inner_join(tmp2, by = "col") %>%
  select(station_id, nearest) %>%
  unique() -> df.bei.grid.nearest
rm(tmp1, tmp2, df.tmp)
```

## London the nearest Grid point

```{r}
df.lon.station %>% filter(need_prediction == "TRUE") %>% select(station_id, long, lati) %>% mutate(group = "target") -> tmp1
df.lon.grid.meo %>% select(stationName, long, lati) %>% unique() %>% mutate(group = "grid") %>% rename(station_id = "stationName") -> tmp2
df.tmp <- bind_rows(tmp1, tmp2) %>% mutate(number = row_number())
rm(tmp1, tmp2)
dist.matrix <- df.tmp %>% select(long, lati) %>% as.matrix() %>% dist() 
reshape::melt(as.matrix(dist.matrix), varnames = c("row", "col")) %>%
  filter(value != 0) %>%
  filter(col > 13) %>% #13までがtargetなのでそれを除く
  filter(row <= 13) %>% #13までがtargetなのでそれを除く
  group_by(row) %>%
  dplyr::summarise(col = col[which.min(value)], min_dist = min(value)) -> df.min.dist

df.tmp %>%
  select(station_id, number) %>%
  inner_join(df.min.dist, by = c("number" = "row")) %>%
  select(-number) -> tmp1
df.tmp %>%
  select(station_id, number) %>%
  setnames("station_id", "nearest") %>%
  inner_join(df.min.dist, by = c("number" = "col")) %>%
  select(nearest, number) %>%
  setnames("number", "col") -> tmp2
tmp1 %>%
  inner_join(tmp2, by = "col") %>%
  select(station_id, nearest) %>%
  unique() -> df.lon.grid.nearest
rm(tmp1, tmp2, df.tmp)
```

## Beijing weather Join

```{r}
df.bei.aq %>%
  inner_join(df.bei.grid.nearest, by = "station_id") %>%
  left_join(df.bei.grid.meo, by = c("nearest" = "stationName", "utc_time")) %>%
  select(-nearest, -long, -lati) %>%
  rename(grid1_temperature = "temperature",
         grid1_pressure = "pressure",
         grid1_humidity = "humidity",
         grid1_wind_direction = "wind_direction",
         grid1_wind_speed = "wind_speed") -> df.bei.aq.weather

df.bei.aq.weather %>%
  inner_join(df.bei.obs.nearest, by = "station_id") %>%
  left_join(df.bei.obs.meo, by = c("nearest" = "station_id", "utc_time")) %>%
  select(-nearest, -long, -lati) %>%
  rename(obs1_temperature = "temperature",
         obs1_pressure = "pressure",
         obs1_humidity = "humidity",
         obs1_wind_direction = "wind_direction",
         obs1_wind_speed = "wind_speed",
         obs1_weather = "weather") -> df.bei.aq.weather
```

## London weather Join

```{r}
df.lon.aq1 %>%
  inner_join(df.lon.grid.nearest, by = "station_id") %>%
  left_join(df.lon.grid.meo, by = c("nearest" = "stationName", "utc_time")) %>%
  select(-nearest, -long, -lati) %>%
  rename(grid1_temperature = "temperature",
         grid1_pressure = "pressure",
         grid1_humidity = "humidity",
         grid1_wind_direction = "wind_direction",
         grid1_wind_speed = "wind_speed") -> df.lon.aq1.weather
```

## Save1

```{r}
write.table(df.bei.aq, paste0(DIR_OUTPUT_CLEAN,"/original_bei_aq.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.bei.aq, paste0(DIR_OUTPUT_CLEAN,"/original_bei_aq.RDS"))
write.table(df.lon.aq1, paste0(DIR_OUTPUT_CLEAN,"/original_lon_aq1.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.lon.aq1, paste0(DIR_OUTPUT_CLEAN,"/original_lon_aq1.RDS"))
write.table(df.lon.aq2, paste0(DIR_OUTPUT_CLEAN,"/original_lon_aq2.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.lon.aq2, paste0(DIR_OUTPUT_CLEAN,"/original_lon_aq2.RDS"))

write.table(df.bei.aq.weather, paste0(DIR_OUTPUT_CLEAN,"/original_bei_aq_weather.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.bei.aq.weather, paste0(DIR_OUTPUT_CLEAN,"/original_bei_aq_weather.RDS"))
write.table(df.lon.aq1.weather, paste0(DIR_OUTPUT_CLEAN,"/original_lon_aq1_weather.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.lon.aq1.weather, paste0(DIR_OUTPUT_CLEAN,"/original_lon_aq1_weather.RDS"))

write.table(df.bei.obs.nearest, paste0(DIR_OUTPUT_CLEAN,"/bei_obs_nearest.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.bei.obs.nearest, paste0(DIR_OUTPUT_CLEAN,"/bei_obs_nearest.RDS"))
write.table(df.bei.grid.nearest, paste0(DIR_OUTPUT_CLEAN,"/bei_grid_nearest.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.bei.grid.nearest, paste0(DIR_OUTPUT_CLEAN,"/bei_grid_nearest.RDS"))
write.table(df.lon.grid.nearest, paste0(DIR_OUTPUT_CLEAN,"/lon_grid_nearest.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.lon.grid.nearest, paste0(DIR_OUTPUT_CLEAN,"/lon_grid_nearest.RDS"))

#save(list=ls(), file="all.Rdata")
```

## Bind AQ and Weather original and api 

```{r}
df.api.bei.aq %>%
  inner_join(df.bei.grid.nearest, by = "station_id") %>%
  left_join(df.api.bei.grid.meo, by = c("nearest" = "stationName", "utc_time")) %>%
  select(-nearest) %>%
  rename(grid1_temperature = "temperature",
         grid1_pressure = "pressure",
         grid1_humidity = "humidity",
         grid1_wind_direction = "wind_direction",
         grid1_wind_speed = "wind_speed",
         grid1_weather = "weather") -> df.api.bei.aq.weather

df.api.bei.aq.weather %>%
  inner_join(df.bei.obs.nearest, by = "station_id") %>%
  left_join(df.api.bei.obs.meo, by = c("nearest" = "stationName", "utc_time")) %>%
  select(-nearest) %>%
  rename(obs1_temperature = "temperature",
         obs1_pressure = "pressure",
         obs1_humidity = "humidity",
         obs1_wind_direction = "wind_direction",
         obs1_wind_speed = "wind_speed",
         obs1_weather = "weather") -> df.api.bei.aq.weather

df.api.ld.aq %>%
  inner_join(df.lon.grid.nearest, by = "station_id") %>%
  left_join(df.api.ld.grid.meo, by = c("nearest" = "stationName", "utc_time")) %>%
  select(-nearest) %>%
  rename(grid1_temperature = "temperature",
         grid1_pressure = "pressure",
         grid1_humidity = "humidity",
         grid1_wind_direction = "wind_direction",
         grid1_wind_speed = "wind_speed",
         grid1_weather = "weather") -> df.api.ld.aq.weather

df.bei.aq <- bind_rows(df.bei.aq.weather, df.api.bei.aq.weather) %>% unique() %>% arrange(station_id)
stations <- unique(df.lon.aq1$station_id)
df.lon.aq1 <- bind_rows(df.lon.aq1.weather, filter(df.api.ld.aq.weather, station_id %in% stations)) %>% unique() %>% arrange(station_id)
```

## Save2

```{r}
write.table(df.bei.aq, paste0(DIR_OUTPUT_CLEAN,"/api_bind_bei_aq.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.bei.aq, paste0(DIR_OUTPUT_CLEAN,"/api_bind_bei_aq.RDS"))
write.table(df.lon.aq1, paste0(DIR_OUTPUT_CLEAN,"/api_bind_lon_aq1.tsv"), sep = "\t", quote = F, row.names = F)
saveRDS(df.lon.aq1, paste0(DIR_OUTPUT_CLEAN,"/api_bind_lon_aq1.RDS"))
```

## Time trancate

```{r}
df.bei.aq %<>% trancateTime("utc_time")
df.lon.aq1 %<>% trancateTime("utc_time")
df.lon.aq2 %<>% trancateTime("utc_time")
```

## Submit File

```{r}
df.submit %>%
  tidyr::separate(test_id, c("basho","hour"), sep = "#") -> df.submit.clean
```

# Map  {.tabset .tabset-fade .tabset-pills}

## Beijing 
- 予測対象は35 Stations
- Observedは18箇所で測定してる
- Gridは651箇所で測定してる

```{r}
df.bei.station %>% select(station_id, long, lati) %>% mutate(group = "target") -> tmp1
df.bei.obs.meo %>% select(station_id, long, lati) %>%  unique() %>% mutate(group = "obs") -> tmp2
df.bei.grid.meo %>% select(stationName, long, lati) %>% unique() %>% mutate(group = "grid") %>% rename(station_id = "stationName") -> tmp3
df.color <- data.frame(group = c("target","obs","grid"), color = c(drsimonj_cols("red"),  drsimonj_cols("blue"),  drsimonj_cols("green")), stringsAsFactors = F)
tmp1 %>%
  bind_rows(tmp2) %>%
  bind_rows(tmp3) %>%
  inner_join(df.color, by = "group") %>%
  mutate(number = row_number()) %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(~long, ~lati, label = ~as.character(station_id)) %>%
  addCircleMarkers(~long, ~lati, color = ~color)
rm(tmp1,tmp2,tmp3)
```

## London
- 予測対象は13 Stations
- 非予測対象は11 Stations
- Gridは861箇所で測定してる

```{r}
df.lon.station %>% filter(need_prediction == "TRUE") %>% select(station_id, long, lati) %>% mutate(group = "target") -> tmp1
df.lon.station %>% filter(is.na(.$need_prediction)) %>% select(station_id, long, lati) %>% mutate(group = "non_target") -> tmp2
df.lon.grid.meo %>% select(stationName, long, lati) %>% unique() %>% mutate(group = "grid") %>% rename(station_id = "stationName") -> tmp3
df.color <- data.frame(group = c("target","non_target","grid"), color = c(drsimonj_cols("red"),  drsimonj_cols("blue"),  drsimonj_cols("green")), stringsAsFactors = F)
tmp1 %>%
  bind_rows(tmp2) %>%
  bind_rows(tmp3) %>%
  inner_join(df.color, by = "group") %>% 
  mutate(number = row_number()) %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(~long, ~lati, label = ~as.character(station_id)) %>%
  addCircleMarkers(~long, ~lati, color = ~color)
rm(tmp1,tmp2,tmp3)
```

# Overview  {.tabset .tabset-fade .tabset-pills}

## Beijing glimpse 

- 6つの指標（PM2.5, PM10, NO2, CO, O3, SO2）の場所×1時間ごとの値

```{r}
glimpse(df.bei.aq)
```

センサー等で測定しているWeatherデータ。Beijingで18箇所の天気測定結果。2017/1/30 - 2018/1/31 まである

```{r}
glimpse(df.bei.obs.meo)
```

NOAAが提供してるWeatherデータ。Beijingで 651箇所の天気測定結果。1時間ごとに2017/1/1 - 2018/3/27 まである

```{r}
glimpse(df.bei.grid.meo)
```

## London glimpse 

Londonのどの地域を予測するかを記したデータ

```{r}
print(df.lon.station)
```

3つの指標（PM2.5, PM10, NO2）の場所×1時間ごとの値

```{r}
glimpse(df.lon.aq1)
```

- 3つの指標（PM2.5, PM10, NO2）の場所×1時間ごとの値

```{r}
glimpse(df.lon.aq2)
```

NOAAが提供してるWeatherデータ。Londonで 861箇所の天気測定結果。1時間ごとに2017/1/1 - 2018/3/27 まである

```{r}
glimpse(df.lon.grid.meo)
```

## Start and End Date

```{r}
print(paste0("Bei AQ Start : ", min(df.bei.aq$utc_time), " End : ", max(df.bei.aq$utc_time)))
print(paste0("Bei Obs MEO Start : ", min(df.bei.obs.meo$utc_time), " End : ", max(df.bei.obs.meo$utc_time)))
print(paste0("Bei Grid MEO Start : ", min(df.bei.grid.meo$utc_time), " End : ", max(df.bei.grid.meo$utc_time)))
print(paste0("Lon AQ1 Start : ", min(df.lon.aq1$utc_time), " End : ", max(df.lon.aq1$utc_time)))
print(paste0("Lon AQ2 Start : ", min(df.lon.aq2$utc_time,na.rm=T), " End : ", max(df.lon.aq2$utc_time,na.rm=T)))
print(paste0("Lon Grid MEO Start : ", min(df.lon.grid.meo$utc_time), " End : ", max(df.lon.grid.meo$utc_time)))
```

## Start and End Date by Station ID

```{r}
stations <- unique(df.bei.aq$station_id)
for(sta in stations){
  df.bei.aq %>%
    filter(station_id == sta) -> tmp
  print(paste0(sta," - Bei AQ Start : ", min(tmp$utc_time), " End : ", max(tmp$utc_time)))
}

stations <- unique(df.lon.aq1$station_id)
for(sta in stations){
  df.lon.aq1 %>%
    filter(station_id == sta) -> tmp
  print(paste0(sta," - Lon AQ1 Start : ", min(tmp$utc_time), " End : ", as.character(max(tmp$utc_time))))
}
```

## Summary

```{r}
summary(df.bei.aq)
```

- 999999(about 900000) is outlier ?
- Difference between NA and 999999 ?
- If the wind speed is less than 0.5m/s (nearly no wind), the value of the wind_direction is 999017.

```{r}
summary(df.bei.obs.meo)
```

- filter 900000

```{r}
df.bei.obs.meo %>%
  filter(temperature < 999999 & humidity < 999999 & wind_direction < 900000) %>% summary
```

## Outlier Count

- 999999 

```{r}
df.bei.obs.meo %>%
  purrr::map_df(function(x) sum(x == 999999.0, na.rm = T)) %>%
  gather(feature, num_outliers) %>%
  mutate(percent = num_outliers/nrow(df.bei.obs.meo))
```

## Null Count

`aq` data

```{r}
df.bei.aq %>%
  purrr::map_df(function(x) sum(is.na(x))) %>%
  gather(feature, num_nulls) %>%
  mutate(percent = num_nulls/nrow(df.bei.aq))
```

`meo` data

```{r}
df.bei.obs.meo %>%
  purrr::map_df(function(x) sum(is.na(x))) %>%
  gather(feature, num_nulls) %>%
  mutate(percent = num_nulls/nrow(df.bei.obs.meo))
```

## Null Check zhiwuyuan_aq in Beijing

zhiwuyuan_aqだけ異常にNull多い。2017/11ごろから

```{r}
df.bei.aq %>%
  filter(station_id == "zhiwuyuan_aq") %>%
  filter(is.na(.$PM2.5)) -> tmp
unique(floor_date(tmp$utc_time,"1 day"))
```

## Beijing Data Table

```{r}
DT::datatable(df.bei.aq %>% head(100))
DT::datatable(df.bei.obs.meo %>% head(100))
DT::datatable(df.bei.grid.meo %>% head(100))
```

## London Data Table

```{r}
DT::datatable(df.lon.aq1 %>% head(100))
DT::datatable(df.lon.aq2 %>% head(100))
DT::datatable(df.lon.grid.meo %>% head(100))
```

## Beijing station_id

`aq` データにあるBeijingの35地点全部予測すればOK

```{r}
print(paste0("num:", length(unique(df.bei.aq$station_id))))
print(unique(df.bei.aq$station_id))
```

## London station_id

`aq1` データにあるLondonの13地点全部予測すればOK

```{r}
print(paste0("num:", length(unique(df.lon.aq1$station_id))))
print(unique(df.lon.aq1$station_id))
```

## Submit Data 

48箇所ある

```{r}
plyr::count(df.submit.clean$basho)
```

```{r}
plyr::count(df.submit.clean$hour)
```


# Categorical feature statistics {.tabset .tabset-fade .tabset-pills}

## Station ID Count 

`aq`は`station_id`ごとにばらつきはなく8886レコードある

```{r}
plyr::count(df.bei.aq$station_id) %>% DT::datatable()
```

`meo`は`statiton_id`に若干ばらつき

```{r}
plyr::count(df.bei.obs.meo$station_id) %>% DT::datatable()
```

## Weather Count 

- `Sunny/clean` is 75%
- `Haze` is 17%
- `Fog` is 6%
- `Rain` is 1%
- `Dust` may be related to target values

```{r}
plyr::count(df.bei.obs.meo$weather) %>% arrange(desc(freq)) %>% mutate(percent = freq/nrow(df.bei.obs.meo))
```

# Numerical feature Density : AQ {.tabset .tabset-fade .tabset-pills}

```{r, results='asis', fig.height=20}
group <- "station_id"
for(target in c("PM2.5","PM10","NO2","CO","O3","SO2")){
  g <- ggplot(df.bei.aq, aes_string(x = target, group = group, color = group)) + geom_density() + facet_wrap(~station_id, ncol = 3) + guides(color = FALSE)
  cat('\n')
  cat("## ", target," \n")
  print(g)
  cat('\n')
}
```

# Numerical feature Density : MEO {.tabset .tabset-fade .tabset-pills}

```{r, results='asis', fig.height=20}
group <- "station_id"
tmp.df <- df.bei.obs.meo %>% filter(temperature < 999999 & humidity < 999999 & wind_direction < 900000)
for(target in c("temperature","pressure","humidity","wind_direction","wind_speed")){
  g <- ggplot(tmp.df, aes_string(x = target, group = group, color = group)) + geom_density() + facet_wrap(~station_id, ncol = 3) + guides(color = FALSE) 
  cat('\n')
  cat("## ", target," \n")
  print(g)
  cat('\n')
}

```

# Beijing Time Series Analysis {.tabset .tabset-fade .tabset-pills}

## Setting

```{r}
X_TARGET <- "utc_time"
Y_TARGETS <- c("PM2.5","PM10","NO2","CO","O3","SO2")
DATE_SET <- c("12 hour")
FUNC <- function(x){mean(x, na.rm=T)}
df <- df.bei.aq
```

```{r, results="asis"}
for(yt in Y_TARGETS){
  for(ds in DATE_SET){
    dt <- "new_date"
    df$new_date <- floor_date(df[,X_TARGET], ds)
    df.tmp <- group_by(df, new_date) %>% dplyr::summarise_at(vars(contains(yt, ignore.case=TRUE)), FUNC) %>% as.data.frame() # data frame型にしたいため（調べたがこれしかないっぽい）
    if(is.numeric(df.tmp[,yt])){
      g <- ggplot(df.tmp, aes_string(x = dt, y = yt)) + geom_line() + geom_point(shape = 21, size = 1)
      cat('\n')
      cat("## Y軸：", yt, "　X軸の単位：",ds, "\n")
      print(g)
      cat('\n')
    }
  }
}
```

# Beijing Time Series Analysis by station_id {.tabset .tabset-fade .tabset-pills}

## Setting

```{r}
X_TARGET <- "utc_time"
stations <- unique(df.bei.aq$station_id)
DATE_SET <- c("12 hour")
df.bei.aq %>%
  select(station_id, utc_time, PM2.5, PM10, NO2, CO, O3, SO2) %>%
  gather(dimension, value, -utc_time, -station_id) -> df
```

```{r, fig.height = 12, results="asis"}
for(sta in stations){
  for(ds in DATE_SET){
    dt <- "new_date"
    df %>%
      filter(station_id == sta) %>%
      mutate(new_date = floor_date(utc_time, ds)) %>%
      group_by(new_date, dimension) %>%
      dplyr::summarise(value = mean(value, na.rm = T)) -> df.tmp
    g <- ggplot(df.tmp, aes(x = new_date, y = value, group = dimension, color = dimension)) + geom_line() + geom_point(shape = 21, size = 1) + facet_wrap(~dimension, nrow = 6, ncol = 1, scale = "free_y") + guides(color = F) + labs(x = paste0("X軸の単位:",ds)) + scale_x_datetime(breaks = date_breaks("month"), date_labels = "%m")
    cat('\n')
    cat("## station_id：", sta, "　X軸の単位：",ds, "\n")
    print(g)
    cat('\n')
  }
}
```

# London Time Series Analysis by station_id {.tabset .tabset-fade .tabset-pills}

## Setting

```{r}
X_TARGET <- "utc_time"
stations <- unique(df.lon.aq1$station_id)
DATE_SET <- c("12 hour")
df.lon.aq1 %>%
  select(station_id, utc_time, PM2.5, PM10, NO2) %>%
  gather(dimension, value, -utc_time, -station_id) -> df
```


```{r, fig.height = 12, results="asis"}
for(sta in stations){
  for(ds in DATE_SET){
    dt <- "new_date"
    df %>%
      filter(station_id == sta) %>%
      mutate(new_date = floor_date(utc_time, ds)) %>%
      group_by(new_date, dimension) %>%
      dplyr::summarise(value = mean(value, na.rm = T)) -> df.tmp
    g <- ggplot(df.tmp, aes(x = new_date, y = value, group = dimension, color = dimension)) + geom_line() + geom_point(shape = 21, size = 1) + facet_wrap(~dimension, nrow = 6, ncol = 1, scale = "free_y") + guides(color = F) + labs(x = paste0("X軸の単位:",ds)) + scale_x_datetime(breaks = date_breaks("month"), date_labels = "%m")
    cat('\n')
    cat("## station_id：", sta, "　X軸の単位：",ds, "\n")
    print(g)
    cat('\n')
  }
}
```

# Beijing Time Series Autocorrelation by station_id {.tabset .tabset-fade .tabset-pills}

```{r, results="asis"}
#ccf(bbb$PM2.5, bbb$NO2)
stations <- unique(df.bei.aq$station_id)
targets <- c("PM2.5","PM10","O3")
for(s in stations){
  df.bei.aq %>%
    filter(station_id == s) %>%
    dplyr::arrange(utc_time) %>%
    select(-utc_time) -> tmp1
  for(target in targets){
    tmp1 %>%
      select_(target) %>%
      na.omit() -> tmp2
    a <- acf(tmp2[[target]], lag.max = 24 * 30, type = "correlation", plot = F)
    cat('\n')
    cat("## station_id：", s, "　Y：",target, "\n")
    plot(a)
    cat('\n')
  }
}
```

# London Time Series Autocorrelation by station_id {.tabset .tabset-fade .tabset-pills}

```{r, results="asis"}
#ccf(bbb$PM2.5, bbb$NO2)
stations <- unique(df.lon.aq1$station_id)
targets <- c("PM2.5","PM10")
for(s in stations){
  df.lon.aq1 %>%
    filter(station_id == s) %>%
    dplyr::arrange(utc_time) %>%
    select(-utc_time) -> tmp1
  for(target in targets){
    tmp1 %>%
      select_(target) %>%
      na.omit() -> tmp2
    a <- acf(tmp2[[target]], lag.max = 24 * 30, type = "correlation", plot = F)
    cat('\n')
    cat("## station_id：", s, "　Y：",target, "\n")
    plot(a)
    cat('\n')
  }
}
```

# Beijing Cross correlation {.tabset .tabset-fade .tabset-pills}

```{r, results="asis"}
cat('\n')
cat("## All \n")
df.bei.aq %>% 
  select(PM2.5, PM10, NO2, CO, O3, SO2)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")
cat('\n')

stations <- unique(df.bei.aq$station_id)
for(s in stations){
  #s <- "aotizhongxin_aq"
  cat('\n')
  cat(paste0("## station_id：",s, "\n"))
  df.bei.aq %>% 
    filter(station_id == s) %>%
    select(PM2.5, PM10, NO2, CO, O3, SO2) %>%
    cor(use="pairwise.complete.obs", method = "pearson") %>%
    corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")
  cat('\n')
}
```

# London Cross correlation {.tabset .tabset-fade .tabset-pills}

```{r, results="asis"}
cat('\n')
cat("## All \n")
df.lon.aq1 %>% 
  select(PM2.5, PM10, NO2)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")
cat('\n')

stations <- unique(df.lon.aq1$station_id)
for(s in stations){
  #s <- "aotizhongxin_aq"
  cat('\n')
  cat(paste0("## station_id：",s, "\n"))
  df.lon.aq1 %>% 
    filter(station_id == s) %>%
    select(PM2.5, PM10, NO2) %>%
    cor(use="pairwise.complete.obs", method = "pearson") %>%
    corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")
  cat('\n')
}
```

# Beijing Time Trancate Analysis {.tabset .tabset-fade .tabset-pills}

## Beijing year month

```{r}
df <- df.bei.aq
```

```{r}
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(year_month = paste(.$year,formatC(.$month,width=2, flag="0"), sep = "-")) %>%
  ggplot(aes(x = year_month, y = PM2.5)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(year_month = paste(.$year,formatC(.$month,width=2, flag="0"), sep = "-")) %>%
  ggplot(aes(x = year_month, y = PM10)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(year_month = paste(.$year,formatC(.$month,width=2, flag="0"), sep = "-")) %>%
  ggplot(aes(x = year_month, y = O3)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Beijing week_num_of_year

```{r, out.width='\\maxwidth'}
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(week_num_of_year = paste(.$year,formatC(.$month,width=2, flag="0"),formatC(.$week_num_of_year, width=2,flag="0"), sep = "-")) %>%
  ggplot(aes(x = week_num_of_year, y = PM2.5)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(week_num_of_year = paste(.$year,formatC(.$month,width=2, flag="0"),formatC(.$week_num_of_year, width=2,flag="0"), sep = "-")) %>%
  ggplot(aes(x = week_num_of_year, y = PM10)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(week_num_of_year = paste(.$year,formatC(.$month,width=2, flag="0"),formatC(.$week_num_of_year, width=2,flag="0"), sep = "-")) %>%
  ggplot(aes(x = week_num_of_year, y = O3)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Beijing day

```{r}
df %>%
  mutate(day = formatC(.$day,width=2,flag="0")) %>%
  ggplot(aes(x = day, y = PM2.5)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(day = formatC(.$day,width=2,flag="0")) %>%
  ggplot(aes(x = day, y = PM10)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(day = formatC(.$day,width=2,flag="0")) %>%
  ggplot(aes(x = day, y = O3)) + geom_boxplot(outlier.colour = "red")
```

## Beijing wday

```{r}
df %>%
  mutate(wday = formatC(.$wday,width=2,flag="0")) %>%
  ggplot(aes(x = wday, y = PM2.5)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(wday = formatC(.$wday,width=2,flag="0")) %>%
  ggplot(aes(x = wday, y = PM10)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(wday = formatC(.$wday,width=2,flag="0")) %>%
  ggplot(aes(x = wday, y = O3)) + geom_boxplot(outlier.colour = "red")
```

## Beijing Hour

```{r}
df %>%
  mutate(hour = formatC(.$hour,width=2,flag="0")) %>%
  ggplot(aes(x = hour, y = PM2.5)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(hour = formatC(.$hour,width=2,flag="0")) %>%
  ggplot(aes(x = hour, y = PM10)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(hour = formatC(.$hour,width=2,flag="0")) %>%
  ggplot(aes(x = hour, y = O3)) + geom_boxplot(outlier.colour = "red")
```

# London Time Trancate Analysis {.tabset .tabset-fade .tabset-pills}

## London year month

```{r}
df <- df.lon.aq1
```

```{r}
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(year_month = paste(.$year,formatC(.$month,width=2, flag="0"), sep = "-")) %>%
  ggplot(aes(x = year_month, y = PM2.5)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(year_month = paste(.$year,formatC(.$month,width=2, flag="0"), sep = "-")) %>%
  ggplot(aes(x = year_month, y = PM10)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## London week_num_of_year

```{r, out.width='\\maxwidth'}
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(week_num_of_year = paste(.$year,formatC(.$month,width=2, flag="0"),formatC(.$week_num_of_year, width=2,flag="0"), sep = "-")) %>%
  ggplot(aes(x = week_num_of_year, y = PM2.5)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
df %>%
  mutate(year = year(utc_time)) %>%
  mutate(week_num_of_year = paste(.$year,formatC(.$month,width=2, flag="0"),formatC(.$week_num_of_year, width=2,flag="0"), sep = "-")) %>%
  ggplot(aes(x = week_num_of_year, y = PM10)) + geom_boxplot(outlier.colour = "red") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## London day

```{r}
df %>%
  mutate(day = formatC(.$day,width=2,flag="0")) %>%
  ggplot(aes(x = day, y = PM2.5)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(day = formatC(.$day,width=2,flag="0")) %>%
  ggplot(aes(x = day, y = PM10)) + geom_boxplot(outlier.colour = "red")
```

## London wday

```{r}
df %>%
  mutate(wday = formatC(.$wday,width=2,flag="0")) %>%
  ggplot(aes(x = wday, y = PM2.5)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(wday = formatC(.$wday,width=2,flag="0")) %>%
  ggplot(aes(x = wday, y = PM10)) + geom_boxplot(outlier.colour = "red")
```

## London Hour

```{r}
df %>%
  mutate(hour = formatC(.$hour,width=2,flag="0")) %>%
  ggplot(aes(x = hour, y = PM2.5)) + geom_boxplot(outlier.colour = "red")
df %>%
  mutate(hour = formatC(.$hour,width=2,flag="0")) %>%
  ggplot(aes(x = hour, y = PM10)) + geom_boxplot(outlier.colour = "red")
```

# Weather {.tabset .tabset-fade .tabset-pills}

## Beijing Grid Weather Mean and Median

天気との関連はあり

```{r}
mean_na <- function(x){mean(x, na.rm = T)}
median_na <- function(x){median(x, na.rm = T)}
df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(grid1_weather, PM2.5, PM10, O3, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  group_by(grid1_weather) %>%
  dplyr::summarise_all(funs(median_na))

df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(grid1_weather, PM2.5, PM10, O3, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  group_by(grid1_weather) %>%
  dplyr::summarise_all(funs(mean_na))
```

## Beijing Obs Weather Mean and Median

天気との関連はあり

```{r}
mean_na <- function(x){mean(x, na.rm = T)}
median_na <- function(x){median(x, na.rm = T)}
df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(obs1_weather, PM2.5, PM10, O3)  %>%
  group_by(obs1_weather) %>%
  dplyr::summarise_all(funs(median_na))

df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(obs1_weather, PM2.5, PM10, O3)  %>%
  group_by(obs1_weather) %>%
  dplyr::summarise_all(funs(mean_na))
```


## Beijing Relation with Targets

O3とgrid1_temp / grid1_wind_speed が強いか

```{r}
df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(PM2.5, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")

df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(PM10, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")

df.bei.aq %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(O3, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")
```

## Beijing Relation between obs and grid

```{r}
df.bei.aq %>%
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  replace_na(list(obs1_weather = "unknown")) %>%
  replace_na(list(grid1_weather = "unknown")) %>%
  group_by(obs1_weather, grid1_weather) %>%
  dplyr::count() %>%
  ungroup() %>%
  spread(grid1_weather, n) -> tmp
row.names(tmp) <- tmp$obs1_weather
tmp <- select(tmp, -obs1_weather)
pheatmap(tmp, cluster_row = FALSE, cluster_col = FALSE, display_numbers = TRUE, legend = T)
```

## London Weather Mean and Median

天気との関連はあり

```{r}
mean_na <- function(x){mean(x, na.rm = T)}
median_na <- function(x){median(x, na.rm = T)}
df.lon.aq1 %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(grid1_weather, PM2.5, PM10, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  group_by(grid1_weather) %>%
  dplyr::summarise_all(funs(median_na))

df.lon.aq1 %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(grid1_weather, PM2.5, PM10, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  group_by(grid1_weather) %>%
  dplyr::summarise_all(funs(mean_na))
```


## London Relation with Targets

相関が小さい

```{r}
df.lon.aq1 %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(PM2.5, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")

df.lon.aq1 %>% 
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  select(PM10, grid1_temperature, grid1_pressure, grid1_humidity, grid1_wind_direction, grid1_wind_speed)  %>%
  cor(use="pairwise.complete.obs", method = "pearson") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE, method = "number")
```


## London weather grid

weatherの扱いむずいな…

```{r}
df.lon.aq1 %>%
  filter(utc_time >= as.POSIXct("2018-02-01", "UTC")) %>%
  replace_na(list(grid1_weather = "unknown")) %>%
  group_by(grid1_weather) %>%
  dplyr::count() %>%
  ggplot(aes(x = grid1_weather, y = log10(n), fill = grid1_weather)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Next Steps

- Null Time by each dimension


